### 2019-09-17 2019_neurips_vigil/experiments.tex
overall accuracy comparison

@@

\begin{figure}
	\centering
	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset. We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard. }
	\resizebox{6cm}{4.5cm}{%

		\begin{tikzpicture}

		\tiny

		\begin{axis}[
		ybar,
		enlargelimits=0.15,
		legend style={at={(0.5,-0.15)},
			anchor=north,legend columns=-1},
		ylabel={COG test accuracy in \% },
		symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
		xtick=data,
		nodes near coords,
		nodes near coords align={vertical},
		]
		\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
		\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
		\legend{SAMNet ,COG Model}
		\end{axis}
		\end{tikzpicture}
	}
\end{figure}

>>>>

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\textwidth]{results/samnet_cog_overall_transfer.png}
	\caption{Comparison of SAMNet (blue) and COG model (gray) on their abilities to generalize from the canonical to the hard dataset. Light gray indicates original results, whereas right gray indicates the accuracy of COG models that we have trained on our own using the original code.}
	\label{fig:samcell}
\end{wrapfigure}

@@
